\vskip-0.6in \Large Political Uncertainty

### 2015-09-25 GS-extension.tex
substitute correct combining of FOCs in 'math for discrete model' section

\newpage
\subsection{Math for Discrete Model}
The math that follows from Equation \ref{eq:logistic}:
\begin{itemize}
	\item Let
		\begin{enumerate}
			\item $X = -\alpha + b(0)$ 
			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
		\end{enumerate}
	\item Then Equation \ref{eq:logistic} is equivalent to:
		\begin{equation}
			\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z} }
					\label{eq:logistic2}
		\end{equation}
		\[
			\frac{2 + e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\[
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\begin{equation}
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Likewise, we have
		\begin{equation}
			\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Setting the left-hand size of these two equations equal to each other,
		\[
		  \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
		\]
		\[
		  \frac{e^{-X-Z} + e^{-Y-Z}}{1+e^{-Z}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
		\]
		\[
		  e^{-X-Z} + e^{-Y-Z} + e^{-X-Y-Z} +e^{-2Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-X-Y-Z} +e^{-Y-2Z}
		\]
		\[
		  e^{-X-Z} +e^{-2Y-Z}= e^{-X-Y} +e^{-Y-2Z}
		\]
		\[
		  e^{-X}\left(e^{-Z} - e^{-Y} \right) = e^{-Y-Z}\left(e^{-Z} - e^{-Y} \right)
		\]

\subsection{Second Order Condition}
Perhaps more importantly, let's look at the second order condition (using the same substitutions at the top of the previous page). The first derivative of the objective function w.r.t. $b(-\frac{1}{2})$ is (in logistic form)
\begin{equation}
  W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} \right] - 1
\end{equation}
\begin{equation}
  W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] - 1
	\label{eq:firstderiv}
\end{equation}
Now, the second derivative:
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} 2\left(1+e^{-Z}\right) e^{-Z}-\left(1+e^{-Z}\right)^2 e^{-Z}}{\left(1+e^{-Z}\right)^4} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} 2 e^{-Z}-\left(1+e^{-Z}\right) e^{-Z}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} \left\{2 e^{-Z}-\left(1+e^{-Z}\right) \right\}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} \left\{2 e^{-Z}-1-e^{-Z} \right\}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} \left\{e^{-Z}-1 \right\}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z}}{\left(1+e^{-Z}\right)^3} \right] \left\{e^{-Z}-1 \right\}
\]
Everything except for the expression in the curly braces is positive. The expression in the curly braces is positive when $z\leq0$ and negative when $z\geq0$. So this objective function appears to have an inflection point at $z=0$.
\begin{itemize}
	\item When $z < 0$ (as when this legislator is naturally against you and you don't bribe her), this expression is negative
\end{itemize}

>>>>

\newpage
\subsection{Math for Discrete Model}
The math that follows from Equation \ref{eq:logistic}:
\begin{itemize}
	\item Let
		\begin{enumerate}
			\item $X = -\alpha + b(0)$ 
			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
		\end{enumerate}
	\item Then Equation \ref{eq:logistic} is equivalent to:
		\begin{equation}
			\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z} }
					\label{eq:logistic2}
		\end{equation}
		\[
			\frac{2 + e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\[
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\begin{equation}
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Likewise, we have
		\begin{equation}
			\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
		\end{equation}
		and
		\begin{equation}
			\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Setting the left-hand size of these last two equations (the FOCs for the bribes for 0 and $\frac{1}{2}$ equal to each other,
		\[
		  \frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
		\]
		\[
		  \frac{e^{-X-Y} + e^{-X-Z}}{1+e^{-X}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
		\]
		\[
		  e^{-X-Y} + e^{-X-Z} + e^{-X-2Y} +e^{-X-Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-2X-Y} +e^{-X-Y-Z}
		\]
		\[
		  e^{-X-Z} +e^{-X-2Y}= e^{-Y-Z} +e^{-2X-Y}
		\]
		\[
		  e^{-Z} +e^{-2Y}= e^{X-Y-Z} +e^{-X-Y}
		\]
		\begin{equation}
		  e^{Y-Z} +e^{-Y}= e^{X-Z} +e^{-X}
			\label{eq:twoways}
		\end{equation}
   Equation~\ref{eq:twoways} can be rearranged into two similar forms. First:
		\[
		  e^{Y-Z} - e^{X-Z}= e^{-X} - e^{-Y}
		\]
		\[
		  e^{Y} - e^{X}= e^Z\left(e^{-X} - e^{-Y}\right)
		\]
  	Second, multiplying through by zero:
	  \[
		  e^{X} - e^{Y}= e^Z\left(e^{-Y} - e^{-X}\right)
		\]
	\end{itemize}

\newpage		
\subsection{Second Order Conditions}
Perhaps more importantly, let's look at the second order condition (using the same substitutions at the top of the previous page). The first derivative of the objective function w.r.t. $b(-\frac{1}{2})$ is (in logistic form)
\begin{equation}
  W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} \right] - 1
\end{equation}
\begin{equation}
  W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] - 1
	\label{eq:firstderiv}
\end{equation}
Now, the second derivative:
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} 2\left(1+e^{-Z}\right) e^{-Z}-\left(1+e^{-Z}\right)^2 e^{-Z}}{\left(1+e^{-Z}\right)^4} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} 2 e^{-Z}-\left(1+e^{-Z}\right) e^{-Z}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} \left\{2 e^{-Z}-\left(1+e^{-Z}\right) \right\}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} \left\{2 e^{-Z}-1-e^{-Z} \right\}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} \left\{e^{-Z}-1 \right\}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z}}{\left(1+e^{-Z}\right)^3} \right] \left\{e^{-Z}-1 \right\}
\]
Everything except for the expression in the curly braces is positive. The expression in the curly braces is positive when $z\leq0$ and negative when $z\geq0$. So this objective function appears to have an inflection point at $z=0$.
\begin{itemize}
	\item When $z < 0$ (as when this legislator is naturally against you and you don't bribe her), this expression is negative
\end{itemize}
